Optimal Algorithms for Dynamic Balanced Graph Partitioning

### 2020-05-14 paper/disc20clustering.tex
comments

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Fix an input sequence of requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}$.
	Assume on request $\sigma_{t}=\set{u,v}$, 
	i.e., at (time) $t$,
	\RM collocates the pair $\set{u,v}$.
	This means,
	the value of $C_{\set{u,v}}$ at $t$,
	denoted by $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter,
	i.e.,
	$ C^t_{\set{u,v}} = \lambda$.
	We denote the set of all requests to a~pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$ by $\sigma_{\set{x,y}}[t_1,t_2]$,
	and its overall cost to \OPT by
	$\OPT (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.

>>>>

\begin{proof}[Proof of Theorem \ref{thm:k=2}]
	Fix an input sequence of requests
$\sigma:=\{\sigma_1,\dots, \sigma_m\}$.
	Assume that \RM collocates a pair $\set{u,v}$ at time $t$.
	The value of $C_{\set{u,v}}$ at $t$,
	denoted $C^t_{\set{u,v}}$, 
	reaches $\lambda$ immediately before \RM resets the counter.
	For any interval $[t_1,t_2]$, by $\sigma_{\set{x,y}}[t_1,t_2]$ we denote the set of all requests to a~pair $\set{x,y}$ that arrive
	during $[t_1,t_2]$.
	%and its overall cost to \OPT by
	%$\OPT (\sigma_{\{u,v\}}[t_1,t_2])$.
	We may use $\sigma_{\set{x,y}}$ whenever
	 the interval $[t_1,t_2]$ is clear from the context \maciek{As a reader I would be horrified seeing this sentence. Better to fix it in the paragraph}.
	%
	%Else, this is not the first time and
	%Alg collocates $\{u,v\}$ also some time prior to $t$.
